---
title: "00-FocusGroups"
subtitle: "Empathic-dynamics Intervention"
format:
  html:
    self-contained: true
    toc: true
editor: visual
editor_options: 
  chunk_output_type: console
---

```{r, include=F}
library(tidyverse)
library(psych)
library(knitr)
```

```{r, include=F}
data <- read.csv("Focus+Groups_February+13,+2023_11.17.csv")

data <- data[-1,]
data <- data[-1,]
```

```{r, include=F}
data$manager <- factor(data$manager, labels=c("NA","Yes","No"))
```

```{r, include=F}
data$race <- factor(data$race, labels=c("NA", "White/Caucasian","Asian/Asian American","Black/African American", "Hispanic or Latino/a", "Multiracial", "Other"))
```

```{r, include=F}
data$gender <- factor(data$gender, labels=c("NA","Male","Female","Other"))
```

```{r, include=F}
data$ladder <- as.numeric(data$ladder)

data$ed <- factor(data$ed, labels=c("NA", "High school education", "College graduation", "Postgraduate degree"))

data$income <- factor(data$income, labels=c("NA", "$75,001-$100,000", "$100,001-$150,000", "greater than $150,000"))

data$incomeChild <- factor(data$incomeChild, labels=c("NA", "less than $15,000", "$15,000-$30,000", "$30,001-$50,000", "$50,001-$75,000", "$75,001-$100,000", "$100,001-$150,000", "greater than $150,000"))

data$disability_status <- factor(data$disability_status, labels=c("NA", "Yes, Cognitive", "Yes, Emotional", "Yes, Mental", "Yes, Self Identify", "No", "Prefer not to answer"))

data$disability_status <- factor(data$disability_work, labels=c("NA", "Yes", "No", "Prefer not to answer"))

data$job_Years_1 <- as.numeric(data$job_Years_1)

data$employer_Years <- as.numeric(data$employer_Years)

data$age <- as.numeric(data$age)
```

# TL;DR

# Respondent Demographics

We then examine the demographic characteristics of respondents.

Click through the tabs below to see details.

::: panel-tabset
## Managerial Role

We first examine how many participants manage other employees in their current role.

```{r, echo=F, warning=F}
kable(table(data$manager), col.names=c("Do you manage employees?", "n"))
```

## Years of Experience

We then examine number of years spent in their current role.

```{r, echo=F, warning=F}
kable(psych::describe(data$job_Years_1))

ggplot(data, aes(job_Years_1)) +
  geom_density(bins=20, fill="lightblue", alpha=0.8) +
  theme_minimal() +
  xlim(limits=c(1,10)) +
  labs(x = "Number of Years in Current Job",
       y = "Respondents")
```

We then look at years of experience as a UC Berkeley employee more broadly.

```{r, echo=F, warning=F}
kable(psych::describe(data$employer_Years))

ggplot(data, aes(employer_Years)) +
  geom_density(bins=20, fill="lightblue", alpha=0.8) +
  theme_minimal() +
  xlim(limits=c(1,10)) +
  labs(x = "Number of Years Empoyed by UC Berkeley",
       y = "Respondents")
```
:::

::: panel-tabset
## Race

```{r, echo=F}
kable(table(data$race), col.names=c("Race", "n"))
```

## Gender

```{r, echo=F}
kable(table(data$gender), col.names=c("Race", "n"))
```

## SES

```{r, echo=F, warning=F}
kable(table(data$ed), col.names=c("Level of Education", "n"))

ggplot(data, aes(ladder)) +
  geom_density(bins=20, fill="lightblue", alpha=0.8) +
  theme_minimal() +
  xlim(limits=c(1,10)) +
  labs(x = "Ladder Position Chosen",
       y = "Respondents")

kable(table(data$incomeChild), col.names=c("Childhood Income", "n"))
```

## Age

```{r, echo=F, warning=F}
kable(psych::describe(data$age))

ggplot(data, aes(age)) +
  geom_density(bins=20, fill="lightblue", alpha=0.8) +
  theme_minimal() +
  labs(x = "Age",
       y = "Respondents")
```

## Disability Status

```{r, echo=F}
kable(table(data$disability_status), col.names=c("Disability Status", "n"))
```
:::
